Something about Performance, 2D Component of NEMO. (TBC)

### 2015-03-10 nemolite2d_perf.tex
Start new para on parallel efficiency

The simplest OpenMP implementation (black lines) fails to scale beyond
two threads for any of the compilers. However, as soon as a single
PARALLEL region is introduced, the situation is greatly improved with
all three executables now scaling out to at least 12 threads (red
lines). {\bf Add parallel efficiency lines to the OMP scaling plots to
  highlight that things are still not brilliant.}

In restricting ourselves to a single socket, we are keeping all
threads within a single NUMA region. It is therefore surprising that
implementing a `first-touch' policy has any effect and yet, for the
Gnu- and Intel-compiled binaries, it appears to improve performance
when hyperthreading is employed to run on 24 threads (green lines in
Figures~\ref{FIG_gnu_omp_256} and ~\ref{FIG_intel_omp_256}). {\bf Can
  we explain this?}

@@

The final optimisation step that we found to have any significant
effect is to minimise the amount of thread synchronisation by
introducing the NOWAIT qualifier wherever possible (blue lines). For
the Gnu compiler, this improves the performance of the executable on
eight or more threads while, for the Intel compiler, it only gives an
improvement for the 24-thread case. Moving the SINGLE region before a
parallel loop is marginally beneficial for the Gnu- and Cray-compiled
binaries and yet reduces the performance of the Intel binary (purple
lines).

>>>>

The simplest OpenMP implementation (black lines) fails to scale beyond
two threads for any of the compilers. However, as soon as a single
PARALLEL region is introduced, the situation is greatly improved with
all three executables now scaling out to at least 12 threads (red
lines, square symbols). {\bf Add parallel efficiency lines to the OMP
  scaling plots to highlight that things are still not brilliant.}

In restricting ourselves to a single socket, we are keeping all
threads within a single NUMA region. It is therefore surprising that
implementing a `first-touch' policy has any effect and yet, for the
Gnu- and Intel-compiled binaries, it appears to improve performance
when hyperthreading is employed to run on 24 threads (green lines and
diamond symbols in Figures~\ref{FIG_gnu_omp_256} and
~\ref{FIG_intel_omp_256}). {\bf Can we explain this?}

@@

The final optimisation step that we found to have any significant
effect is to minimise the amount of thread synchronisation by
introducing the NOWAIT qualifier wherever possible (blue lines and
upwards-triangle symbols). For the Gnu compiler, this improves the
performance of the executable on eight or more threads while, for the
Intel compiler, it only gives an improvement for the 24-thread
case. Moving the SINGLE region before a parallel loop is marginally
beneficial for the Gnu- and Cray-compiled binaries and yet reduces the
performance of the Intel binary (purple lines and right-pointing
triangles).

In order to quantify the scaling behaviour of the different versions
of nemolite2d with the different compilers/run-time environments, we
also plot the parallel efficiency in
Figures~\ref{FIG_gnu_omp_256},~\ref{FIG_intel_omp_256}
and~\ref{FIG_cray_omp_256}. We define parallel efficiency, $E(n)$, on
a number of threads, $n$, as:
\begin{equation}
E(n) = 100 * \frac{P(n)}{ n*P(1)}
\end{equation}
where $P(n)$ is the performance of the code on $n$ threads.
